Efficient Handling of String-Number Conversion

### 2019-11-22 draft.tex
sec 5

We say that a mapping $I_e:\cvar\cup\#\cvar \rightarrow \nat$ is a \emph{word encoding} a word $w$ (or a $\pa$-encoding of $w$) if $w$ is an instantiation of some parametric word $x \in L(\pa)$ whose Parikh image and interpretation of character variables are defined by $I_e$.  
%
Conversely, $w$ is a \emph{$\pa$-decoding} of $e$.
%
We use $\encode \pa(w)$ below to denote all $\pa$-encodings of a word $w$,
and $\decode \pa (I_e)$ to denote all $\pa$-decodings of a word encoding $e$. Namely,  
% to \emph{word encodings} $e:\cvar\cup\#\cvar \rightarrow \nat$ via the PA $\pa$ and the function $\decode \pa$ does it in the reverse direction.
	$$\encode \pa( w ) = \{e \mid  x \in L(\pa) , I(x) =w, I\in\semof \paf, I_e = I \cup \parikhof{x}\}$$
	$$\decode \pa(I_e) =\{ w \mid x \in L(\pa) , I(x) =w, I\in\semof \paf, I_e = I \cup \parikhof{x} \}$$

@@

If $\pa$ is a PFA, then by Lemma~\ref{lemma:decoding}, each word encoding $e\in \encode \pa( w )$ can be decoded uniquely to the word $w$, i.e.
$$
\{w\} = \decode \pa (\encode \pa (w))
$$
Consequently, as stated by the following corollary of Lemma~\ref{lemma:decoding}, 
Parikh image of parametric words in $L(A)$ paired with character variable interpretations satisfying $\paf$ encode precisely the words in $\semof{\pa}$.
%words in $\semof{\pa}$ are precisely the decodings of the Parikh image of parametric words in $L(A)$ paired with character variables interpretations satisfying $\paf$:

>>>>

We say that a mapping $I_e:\cvar\cup\#\cvar \rightarrow \nat$ is a \emph{word encoding} a word $w$  (or a $\pa$-encoding of $w$) if $w$ is an instantiation of some parametric word $x \in L(\pa)$ whose Parikh image and interpretation of character variables are defined by $I_e$.  
%
Conversely, $w$ is a \emph{$\pa$-decoding} of $I_e$.
%
We use $\encode \pa(w)$ below to denote all $\pa$-encodings of a word $w$,
and $\decode \pa (I_e)$ to denote all $\pa$-decodings of a word encoding $I_e$. Namely,  
% to \emph{word encodings} $e:\cvar\cup\#\cvar \rightarrow \nat$ via the PA $\pa$ and the function $\decode \pa$ does it in the reverse direction.
	$$\encode \pa( w ) = \{I_e \mid  x \in L(\pa) , I(x) =w, I\in\semof \paf, I_e = I \cup \parikhof{x}\}$$
	$$\decode \pa(I_e) =\{ w \mid x \in L(\pa) , I(x) =w, I\in\semof \paf, I_e = I \cup \parikhof{x} \}$$

@@

If $\pa$ is a PFA, then by Lemma~\ref{lemma:decoding}, each word encoding $I_e\in \encode \pa( w )$ can be decoded uniquely to the word $w$, i.e.
$$
\{w\} = \decode \pa (\encode \pa (w))
$$
Consequently, as stated by the following corollary of Lemma~\ref{lemma:decoding}, 
Parikh image of parametric words in $L(A)$ paired with character variable interpretations satisfying $\paf$ encode precisely the words in $\semof{\pa}$.
%words in $\semof{\pa}$ are precisely the decodings of the Parikh image of parametric words in $L(A)$ paired with character variables interpretations satisfying $\paf$:
